Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-22 paper.qmd
Updared gen_axes to remove axes with threshold for distance

gen_axes <- function(proj, limits = 1, axis_pos_x = NULL, axis_pos_y = NULL, axis_labels) {

@@

@@

rows_to_keep <- c(1, 2, 4, 5, 6)

projection_filtered <- projection[rows_to_keep, ]

@@

axes_obj <- gen_axes(
  proj = projection_filtered,
  limits = 1.5,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75,
  axis_labels = paste0("p", rows_to_keep))

>>>>

gen_axes <- function(proj, limits = 1, axis_pos_x = NULL, axis_pos_y = NULL, axis_labels, threshold) {

@@

  ## To remove axes
  axes <- axes |>
    mutate(distance = sqrt((x2 - x1)^2 + (y2 - y1)^2)) |>
    filter(distance >= threshold)

@@

#rows_to_keep <- c(1, 2, 4, 5, 6)

#projection_filtered <- projection[rows_to_keep, ]

@@

axes_obj <- gen_axes(
  proj = projection,
  limits = 1.5,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75,
  axis_labels = names(scaled_pbmc_data),
  threshold = 0.07)
